Instantiating Bunched Dependent Type Theory for Monoidal Classifying Toposes

### 2025-06-11 paper.tex
minor rephrase

\cite{schopp} introduces a bunched dependent type theory, \(\mathbf{BT}(*, 1, \Sigma, \Pi, \Pi^*)\),
of potentially general utility. But they only instantiate it for a single topos: the Schanuel topos.

By stitching together a few results from the literature,
I provide an easy method to verify that \(\mathbf{BT}(*, 1, \Sigma, \Pi, \Pi^*)\)
can be interpreted in a classifying topos of your choice,
so you can start \emph{using} the language as quickly as possible.

>>>>

Dependent type theory, in its standard form, has a model in every topos.
By working within the type theory, you can therefore reason ``internally'' to the topos.

To capture an additional monoidal structure on the topos,
\cite{schopp} extends the type theory to a system they call \(\mathbf{BT}(*, 1, \Sigma, \Pi, \Pi^*)\).
While that paper is specific to the Schanuel topos, the type theory described within is applicable to many others.

I provide an easy method to verify that \(\mathbf{BT}(*, 1, \Sigma, \Pi, \Pi^*)\)
can be interpreted in a classifying topos of your choice,
so you can start \emph{using} the internal language as quickly as possible.
